CONEM2024-0025\\ NEW ABC MULTICRITERIA CLASSIFICATION WITH ANALYTICAL HIERARCHY PROCESS: HOW TO ATTRIBUTE WEIGHTS AND FORCE CONSISTENCY OF PAIRWISE COMPARISONS MATRIX

### 2024-03-13 accepted/CONEM2024/FCPCOM/CONEM2024.tex
updating

@@

    To test the methodology proposed in this article, data were collected from three companies from three different sectors: car mechanics; furniture trades; and plastic packaging manufacturing. Based on the data collected, three benchmarks were developed. The date.txt files corresponding to these three benchmarks are available at https://tbfraga.github.io/COPSolver/ benchmarks/.

@@

@@

>>>>

\usepackage[toc,page]{appendix}
\usepackage{verbatim}
\usepackage{etoolbox}

\makeatletter
\patchcmd{\verbatim@input}{\@verbatim}{\scriptsize\@verbatim}{}{}
\makeatother

@@

    To test the methodology proposed in this article, data were collected for constriction of the pairwise comparison matrix and for ABC classification, using the billing (bl) criterion and other criteria suggested by \cite{FloresWhybark1986}: lead-time (lt); criticality (cr); obsolescence (ob); commonality (cm); substitutability (sb); and repairability (rp). To collect the data, we partnered with three companies from three different sectors: car mechanics; furniture trades; and plastic packaging manufacturing. Based on the data collected, three benchmarks were developed. The date.txt files corresponding to these three benchmarks are available at https://tbfraga.github.io/COPSolver/ benchmarks/.

@@

For analysis of the proposed new methodology for ABC muticriteria classification, we will be focusing on the presentation and analysis of the data provided by the furniture trades company.

The Tab. 2 presents a comparison of the results obtained for the data described above, by ABC classification for the criteria billing and lead time billing. Appendice A presents the file AHP\_Solution.txt, that presents the results found by the module 'COPSolver: library for solving the multicriteria classification problem' - the results generated from the new ABC multicriteria classification with Analitic Hierarch Process and compare it to the ABC classifications of each criterion, for the items ordered in descending order according to the ABC multicriteria classification.

Based on the results presented in these tables, we can verify that the ABC classification, considering only the billing criterion, does not follow the normal pattern defined by the Pareto rule. However, when we use the lead time add-on billing criterion, it is possible to verify that the values are close to what is expected. It is also possible to verify in a very clear way that the approach used to measure the weights of the products produces much more relevant results than the simple random assignment of weights. This approach reduces the viez effect caused by the imbalance of weights and makes the final result carry important qualitative information provided by the responsible official, assigning the appropriate relevance of the different products, as well as the criteria analyzed.

Based on an evaluation of the final results by the participating company, it was possible to verify that these results were very coherent, offering the company very relevant information for the identification of products whose inventory must be maintained, receiving greater attention from the company, as well as for the adoption of more appropriate procedures for the correct control of the different items marketed by the company.

@@

        \begin{appendices}
		\setcounter{section}{0}
		\addtocontents{toc}{\protect\setcounter{tocdepth}{1}}
		\makeatletter
		\addtocontents{toc}{%
		\begingroup
		\let\protect\l@section\protect\l@subsection
}

	\section{AHP\_solution.txt}

	\verbatiminput{files/AHP_solution.txt}

	\addtocontents{toc}{\endgroup}
	\end{appendices}
